The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-08 manuscript/manuscript.Rnw
add expression tree figure

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 3)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ggtree")

@@

<<top.genes.function,echo=FALSE,results="hide">>=
top.genes.table <- function(species.name,n=50) {
    temp <- combined.fpkm[species==species.name &
                      !grepl("^MT-?",gene_short_name) & 
                          !grepl("(RNA\\d|MT)-",human_name)
                          ][order(-mean_fpkm)][!duplicated(gene_short_name)][1:n,list(gene_short_name,human_name,mean_fpkm)]
    setnames(temp,c("Gene name","Human Name","FPKM"))
    if (species.name=="homo sapiens") {
        temp <- temp[,-2,with=FALSE]
    }
    return(temp)
}
@

@@

\begin{wraptable}{L}{0.3\textwidth}
  \tiny
<<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
print(xtable(top.spider.monkey.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.spider.monkey.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 non-mitochondrial genes in
  \textit{Ateles fusciceps}}
\label{tab:top50_spider_monkey_placenta}
\end{wraptable}

@@

\begin{figure}
<<prolactin.evolution.tree,echo=FALSE,fig.width=8,fig.height=8>>=

@@

\begin{figure}
<<galectins.evolution.tree,echo=FALSE,fig.width=8,fig.height=8>>=

>>>>

<<load.libraries,echo=FALSE,results="hide",warning=FALSE,message=FALSE,error=FALSE,cache=FALSE>>=
opts_chunk$set(dev="cairo_pdf",out.width="\\textwidth",out.height="0.7\\textheight",out.extra="keepaspectratio")
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(device = function(file, width = 8, height = 7, ...) {
  cairo_pdf(tempfile(), width = width, height = height, ...)
})
options(scipen = -2, digits = 2)
library("data.table")
library("ggplot2")
library("reshape2")
library("xtable")
library("grid")
library("gridExtra")
library("ape")
library("ggtree")

@@

<<top.genes.function,echo=FALSE,results="hide">>=
top.genes.table <- function(species.name,n=50) {
    temp <- 
        combined.fpkm[species==species.name &
                          !(human_name %in% housekeeping.genes.superset[,gene_short_name]) &
                              !grepl("(RNA\\d|MT)-",human_name)
                      ][order(-mean_fpkm)][!duplicated(gene_short_name)][1:n,list(gene_short_name,
                                                                                  human_name,mean_fpkm)]
    setnames(temp,c("Gene name","Human Name","FPKM"))
    if (species.name=="homo sapiens") {
        temp <- temp[,-2,with=FALSE]
    }
    return(temp)
}
gene.expression <- function(species.name,gene) {
    combined.fpkm[species==species.name &
                      gene_short_name==gene,mean_fpkm]
}

@@

\begin{wraptable}{R}{0.3\textwidth}
  \tiny
<<top.50.spider.monkey.expressed.genes,echo=FALSE,results="asis">>=
top.spider.monkey.genes <- top.genes.table(species.name="ateles fusciceps")
print(xtable(top.spider.monkey.genes),
      booktabs=TRUE,
      floating=FALSE
      )
setkey(top.spider.monkey.genes,"Gene name")
@ 
\caption{Expression in \ac{FPKM} of top 50 non-mitochondrial genes in
  \textit{Ateles fusciceps}}
\label{tab:top50_spider_monkey_placenta}
\end{wraptable}

@@

\begin{figure}
<<prolactin.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=

@@

\begin{figure}
<<galectins.evolution.tree,echo=FALSE,fig.width=12,fig.height=12,warning=FALSE,message=FALSE>>=
